Future challenges for Research Software Engineering

### 2025-04-17 future_challenges_for_RSEng.tex
Add a story part

\subsection{What are new tasks of RTPs?}
\begin{story}{text 1 }{text 2}
 FG-NOTE: RSEs are one type of specialization of RTPs ins science. Do we see any other?
\end{story}

@@

\begin{story}{text 1 }{text 2}
FG-NOTE: By Nick. I've put it here, due to the realtion with the RTP question.
\end{story}

>>>>

\begin{story}{Changes to the Universities}{changes}
 Kim found work years ago at one of the first RSE units in Arcadia. After a couple of years he moved to the university of
Avalon which was interested in setting up their own department for RSEs in order to not fall behind the university of Arcadia.
Kim applies his experiences and improves upon the model set forth by the University of Arcadia. Since the university
of Avalon has to follow different rules not everything can be straightforwardly adapted. Life would be so much easier,
if at least university regulations would be homogenized, no?
\end{story}

\subsection{What are new tasks of RTPs?}
 FG-NOTE: RSEs are one type of specialization of RTPs ins science. Do we see any other?

@@

FG-NOTE: By Nick. I've put it here, due to the realtion with the RTP question.
